---
title: "p8131_hw2_ps3194"
author: "Pangsibo Shen"
date: "2/9/2021"
output: html_document
---

```{r warning=FALSE}
library(tidyverse)
library(ResourceSelection)
```


### Question 1

```{r create dataset}
#Create the bioassay dataset
bioassy_df = tibble(dose = 0:4, n_dying = c(2,8,15,23,27))
```
##### (a)

```{r model fit logit}
#fit the glm with logit link
fit_logit = glm(cbind(n_dying, 30-n_dying) ~ dose, family = binomial(link = 'logit'), data = bioassy_df)
summary(fit_logit)

#calculate the lower and upper bounds of CI
logit_ci_lower = summary(fit_logit)$coefficient[2,1] - qnorm(0.975)*summary(fit_logit)$coefficient[2,2]
logit_ci_higher = summary(fit_logit)$coefficient[2,1] + qnorm(0.975)*summary(fit_logit)$coefficient[2,2]

#Calculate the Deviance
dev_logit = deviance(fit_logit)

#Calculate the p(dying|x=0.01)
predict(fit_logit, tibble(dose = 0.01), type = 'response')
```
The estimate of $\beta_{logit}$ is `r fit_logit$coefficient[2]`, the CI for $\beta_{logit}$ is (`r logit_ci_lower`,`r logit_ci_higher`), the deviance is `r dev_logit` and $\hat{p}(dying|x=0.01)$ = 0.09012.

```{r model fit probit}
#fit the glm with probit link
fit_probit = glm(cbind(n_dying, 30-n_dying) ~ dose, family = binomial(link = 'probit'), data = bioassy_df)
summary(fit_probit)

#calculate the lower and upper bounds of CI
probit_ci_lower = summary(fit_probit)$coefficient[2,1] - qnorm(0.975)*summary(fit_probit)$coefficient[2,2]
probit_ci_higher = summary(fit_probit)$coefficient[2,1] + qnorm(0.975)*summary(fit_probit)$coefficient[2,2]

#Calculate the Deviance
dev_probit = deviance(fit_probit)

#Calculate the p(dying|x=0.01)
predict(fit_probit, tibble(dose = 0.01), type = 'response')
```

The estimate of $\beta_{probit}$ is `r fit_probit$coefficient[2]` and the CI for $\beta_{probit}$ is (`r probit_ci_lower`,`r probit_ci_higher`), the deviance is `r dev_probit` and $\hat{p}(dying|x=0.01)$ = 0.0853078.

```{r model fit c-log-log}
#fit the glm with probit link
fit_cloglog = glm(cbind(n_dying, 30-n_dying) ~ dose, family = binomial(link = 'cloglog'), data = bioassy_df)
summary(fit_cloglog)

#calculate the lower and upper bounds of CI
cloglog_ci_lower = summary(fit_cloglog)$coefficient[2,1] - qnorm(0.975)*summary(fit_cloglog)$coefficient[2,2]
cloglog_ci_higher = summary(fit_cloglog)$coefficient[2,1] + qnorm(0.975)*summary(fit_cloglog)$coefficient[2,2]

#Calculate the Deviance
dev_cloglog = deviance(fit_cloglog)

#Calculate the p(dying|x=0.01)
predict(fit_cloglog, tibble(dose = 0.01), type = 'response')
```

The estimate of $\beta_{cloglog}$ is `r fit_cloglog$coefficient[2]`and the CI for $\beta_{cloglog}$ is (`r cloglog_ci_lower`,`r cloglog_ci_higher`), the deviance is `r dev_cloglog` and $\hat{p}(dying|x=0.01)$ = 0.1281601.

```{r 1a table}
#Generating the table for 1a
table_1a = tibble(Model = c("Estimate of beta", "CI for beta", "Deviance", "p hat"), logit = c(1.1619,"(0.8063,1.517)",0.3787,0.09012), probit = c(0.6864,"(0.4967,0.8760)",0.3137,0.08531), cloglog = c(0.7468,"(0.5323,0.9613)",2.2304,0.1282))

table_1a %>%
  knitr::kable()
```
The logit model has the highest estimate of $\beta$ among three models. The interpretation for $\beta_{logit}$ is that 1 unit increase in dose will increase the log odds of dying by 1.16. Since the probit model has the smallest deviance, hence it may be the best model to fit the data. All three models have the similar predict for $\hat{p}(dying|x=0.01)$.

##### (b)

$$
\begin{split}
g(P(dying) = 0.5) = g(0.5) = \beta_0+ \beta_1, \\
point \ estimate= \hat{x_o} = -\frac{\hat{\beta_0}}{\hat{\beta_1}} \\
logit \ model:g(0.5) = log(0.5/(1-0.5)) = 0 \\
probit \ model:g(0.5) = qnorm(0.5) = 0 \\
C-log-log \ model: log(-log(1-0.5)) = -0.3665
\end{split}
$$

```{r logit LD50}
# LD50 est and CI
beta0_l = fit_logit$coefficients[1]
beta1_l = fit_logit$coefficients[2]
betacov_l = vcov(fit_logit) # inverse fisher information
x0fit_l = -beta0_l/beta1_l

logit_ld50 = exp(x0fit_l)# point estimate of LD50

varx0_l = betacov_l[1,1]/(beta1_l^2) + betacov_l[2,2]*(beta0_l^2)/(beta1_l^4) - 2*betacov_l[1,2]*beta0_l/(beta1_l^3)

logit_ld50_ci = exp(x0fit_l + c(qnorm(0.05),-qnorm(0.05))*sqrt(varx0_l)) # 90% CI for LD50
```

```{r probit LD50}
# LD50 est and CI
beta0_p = fit_probit$coefficients[1]
beta1_p = fit_probit$coefficients[2]
betacov_p = vcov(fit_probit) # inverse fisher information
x0fit_p = -beta0_p/beta1_p

probit_ld50 = exp(x0fit_p)# point estimate of LD50

varx0_p = betacov_p[1,1]/(beta1_p^2) + betacov_p[2,2]*(beta0_p^2)/(beta1_p^4) - 2*betacov_p[1,2]*beta0_p/(beta1_p^3)

fit_probit_ld50_ci = exp(x0fit_p + c(qnorm(0.05),-qnorm(0.05))*sqrt(varx0_p)) # 90% CI for LD50
```

```{r cloglog LD50}
# LD50 est and CI
beta0_c = fit_cloglog$coefficients[1]
beta1_c = fit_cloglog$coefficients[2]
betacov_c = vcov(fit_cloglog) # inverse fisher information
x0fit_c = (-0.3665 - beta0_c)/beta1_c

cloglog_ld50 = exp(x0fit_c)# point estimate of LD50

varx0_c = betacov_c[1,1]/(beta1_c^2) + betacov_c[2,2]*((-0.3665-beta0_c)^2)/(beta1_c^4) - 2*betacov_c[1,2]*(-0.3665-beta0_c)/(beta1_c^3)

cloglog_ld50_ci_1 = exp(x0fit_c + c(qnorm(0.05),-qnorm(0.05))*sqrt(varx0_c)) # 90% CI for LD50
```

```{r 1b table}
#Generating the table for 1b
table_1b = tibble(Model = c("Estimate of LD50", "Lower CI", "Upper CI"), logit = c(logit_ld50,logit_ld50_ci[1],logit_ld50_ci[2]), probit = c(probit_ld50,fit_probit_ld50_ci[1],fit_probit_ld50_ci[2]), cloglog = c(cloglog_ld50,cloglog_ld50_ci_1[1],cloglog_ld50_ci_1[2]))

table_1b %>%
  knitr::kable()
```

---------------------------

### Question 2

```{r}
# create a mph dataframe for question 2
mph_df = tibble(
  amount = seq(from = 10, to = 90, by = 5),
  offer = c(4,6,10,12,39,36,22,14,10,12,8,9,3,1,5,2,1),
  enroll = c(0,2,4,2,12,14,10,7,5,5,3,5,2,0,4,2,1)
)
```

##### (a) How does the model fit the data?

```{r}
fit_2 = glm(cbind(enroll, offer-enroll) ~ amount, family = binomial(link = 'logit'), data = mph_df)
summary(fit_2)
hoslem.test(fit_2$y, fitted(fit_2),g=10)
```
Since from theb hoslem test the p value is greater than 0.05, we reject the null and conclude that the model fits data well.

##### (b) How do you interpret the relationship between the scholarship amount and enrollment rate? What is 95% CI?

```{r}
#coefficient for beta 1
beta_estimate = fit_2$coefficients[2]

#calculate the lower and upper bounds of CI
beta_estimate_ci_lower = summary(fit_2)$coefficient[2,1] - qnorm(0.975)*summary(fit_2)$coefficient[2,2]
beta_estimate_ci_higher = summary(fit_2)$coefficient[2,1] + qnorm(0.975)*summary(fit_2)$coefficient[2,2]

```
The estimate for $\hat{\beta}$ is `r beta_estimate` and the 95% CI is (`r beta_estimate_ci_lower`, `r beta_estimate_ci_higher`) Per $1 increase in scholarship amount,there is an 0.03095043 unit increase in log odds ratio of enrollment rate  

##### (c) How much scholarship should we provide to get 40% yield rate (the percentage of admitted students who enroll?) What is the 95% CI?




